FraCaS: Temporal Analysis

### 2020-11-11 paper2020/paper.tex
improve listing of examples

\section{Examples}
\input{table}

>>>>

\begin{figure*}
\begin{subfigure}{0.5\textwidth}

\fracasex{252}{\answer yes
\item	Since 1992 ITEL has been in Birmingham.
\item	It is now 1996.
\hyp    Itel was in Birmingham in 1993.
} \fracasex{260	}{\answer yes
\item	Yesterday APCOM signed the contract.
\item	Today is Saturday, July 14th.
\hyp    APCOM signed the contract Friday, 13th.

} \fracasex{262	}{\answer yes
\item	Smith left after Jones left.
\item	Jones left after Anderson left.
\hyp    Smith left after Anderson left.

} \fracasex{312	}{\answer yes
\item	ITEL always delivers reports late.
\item	In 1993 ITEL delivered reports.
\hyp    ITEL delivered reports late in 1993.

} \fracasex{320	}{\answer yes
\item	When Jones got his job at the CIA, he knew that he would never be allowed to write his memoirs.
\hyp    It is the case that Jones is not and will never be allowed to write his memoirs.
}

  \caption{Selected correctly handled examples}
  \label{fig:examples}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
{
} \fracasex{259	}{\answer yes
\item	The conference started on July 4th, 1994.
\item	It lasted 2 days.
\hyp    The conference was over on July 8th, 1994.
\failsf Incorrect lexical semantics for ``last $n$ days''.
} \fracasex{294	}{\answer yes
\item	Smith was running his own business in two years.
\hyp    Smith ran his own business.
\failsf Parsing error for ``in two years''
} \fracasex{317	}{\answer yes
\item	Every representative has read this report.
\item	No two representatives have read it at the same time.
\item	No representative took less than half a day to read the report.
\item	There are sixteen representatives.
\hyp    It took the representatives more than a week to read the report.
\failsf Counting semantics not implemented
% } \fracasex{318	}{\answer no
% \item	While Jones was updating the program, Mary came in and told him about the board meeting.
% \item	She finished before he did.
% \hyp    Mary's story lasted as long as Jones's updating the program.
% \failsf Incorrect interaction with anaphora
}
  \caption{Selected incorrectly handled examples.
  We list below a number of selected examples from the temporal section
of the FraCaS testsuite where our semantics fails to list the correct
inference. We list the reason why it fails under the item \textbf{F}.
}
  \label{fig:examples}
\end{subfigure}
\end{figure*}
% \section{Examples}
% \input{table}
